---
title: "Classification of Immission Measurements"
author: "Dr. Alf Loeffler"
date: "10/31/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(lubridate)
```

## Classification of Immission Measurements in Baden Wuertemberg


```{r Glimpse}
BW_Rdat_path<- "~/Documents/Luftqualitaet/Daten/BW_Rdat/"
load(file.path(BW_Rdat_path,"BW_list_tbl.RData"))
summary(BW_list_tbl)%>% kable()
```
22 Sampling stations in Baden-Wuerttemberg have been selected for analysis of concentrations of atmospheric constituents. 3 stations. sampling in rural environments,3 stations located at main streets, 16 sampling urban background immissions
```{r stations,echo = FALSE}
station.names<-names(BW_list_tbl)
rural.stations<- c("Alb","Odw","Sws")
trafic.stations <- c("Lbg_Friedr","Nck","Rt_leder")
urban.backgrd.stations<- station.names%>% setdiff(c(rural.stations,trafic.stations))
print("rural stations :")
print(rural.stations)
print("trafic.stations: ")
print(trafic.stations)
print("urban background:")
print(urban.backgrd.stations)
```
```{r echo =FALSE}
comp_detect <- function(df,cmp) {
  exst<- cmp %in% names(df)
  return(exst)
}
# plot  function for all stations
plt_NO2_trnd <- function(df) {
  df<-df%>% as_tibble()
  ifelse (comp_detect(df,"NO2"),
          {df <- na.omit(df)
  plt <-ggplot(df,aes(x= datetime,y=NO2))+
    geom_point(size = 0.001)+
    geom_smooth(method= "lm",col = "red")+
    ggtitle("NO2-immissions 20 years Trend",
    subtitle = paste(first(df$name),first(df$station)))},NA
    )
  plt
}
plt_NO2_trnd(BW_list_tbl$Stg_Hoh)
```

```{r include=FALSE}
BW_mean_NO2<-map_dbl(BW_list_tbl , function(x) ( ifelse (comp_detect(x,"NO2"),
                                                  mean(x$NO2,na.rm=TRUE),NA)))
BW_median_NO2<- map_dbl(BW_list_tbl,function(x) (ifelse (comp_detect (x,"NO2"),
                                                  median(x$NO2,na.rm=TRUE),NA )))
BW_var_NO2 <- map_dbl(BW_list_tbl, function(x) (ifelse (comp_detect (x,"NO2"),
                                                  var(x$NO2,na.rm=TRUE),NA)))
BW_mean_WG <- map_dbl(BW_list_tbl,function(x) (ifelse (comp_detect (x,"WG"),
                                                  mean(x$WG,na.rm=TRUE),NA )))
BW_var_WG <-map_dbl(BW_list_tbl,function(x) (ifelse(comp_detect (x,"WG"),
                                                  var(x$WG,na.rm=TRUE),NA) ))
BW_mean_O3<-map_dbl(BW_list_tbl , function(x) ( ifelse (comp_detect(x,"O3"),
                                                         mean(x$O3,na.rm=TRUE),NA)))
BW_median_O3<- map_dbl(BW_list_tbl,function(x) (ifelse (comp_detect (x,"O3"),
                                                         median(x$O3,na.rm=TRUE),NA )))
BW_var_O3 <- map_dbl(BW_list_tbl, function(x) (ifelse (comp_detect (x,"O3"),
                                                        var(x$O3,na.rm=TRUE),NA)))

BW_statistic <- tibble (Station =  names(BW_list_tbl),
                                NO2_mean=  BW_mean_NO2,
                                NO2_median=BW_median_NO2,
                                NO2_var =  BW_var_NO2,
                                WG_mean =  BW_mean_WG,
                                WG_var =   BW_var_WG,
                                O3_mean =  BW_mean_O3,
                                O3_median= BW_median_O3,
                                O3_var =   BW_var_O3)
```
Key  immissions data from 22 sampling stations 
```{r echo =FALSE}
BW_statistic%>% arrange(NO2_mean)%>% knitr::kable(digits=1)

```
The table is arranged in ascending order of **mean NO2 immissions measurements** made  and published by LUBW (Landesanstalt für Umwelt Baden Wuerttemberg). In the rural environment 20 year mean immissions are less than  $10 μg/m^3$. the urban background immissions range from $20 [μg/m^3]$. Mean immissions at samplingstations close to main traffic streets are bigger than $40 [μg/m^3]$.








